site_map

### 2020-02-01 SST_patterns.Rmd
update

ggplot(data = signals_average, aes(x = no_of_signals, y = intensity_mean)) +
  geom_point(aes(colour = product), size = 3) +
  geom_smooth(method = "lm") +
  facet_wrap(~site) + 
  labs(x = "Number of signals", y = "Average intensity") +
  scale_colour_Publication()+
  theme_Publication()

@@

>>>>

ggplot(data = signals_average, aes(x = no_of_signals, y = intensity_mean)) +
  geom_point(aes(colour = product), size = 3) +
  geom_smooth(method = "lm") +
  facet_wrap(~site) + 
  labs(x = "Number of signals ", y = "Average intensity (°C)") +
  scale_colour_Publication()+
  theme_Publication()

@@

# Linear model

```{r}
remotes::install_github("moderndive/moderndive")

library(moderndive)
 Regression <- read_csv("Data/Regression.csv")
score_model <- lm(intensity_mean ~ no_of_signals, data = Regression)
final_regression <- get_regression_table(score_model)

  linear_regression <- Regression %>% 
    gather(key = variable, 
           value = value,
           -site) %>%
    group_by(site, variable) %>%
    na.omit() %>% 
    nest() %>%
    mutate(model = purrr::map(data, ~lm(variable ~ value, data = .))) %>%
    unnest(model %>% purrr::map(glance)) %>%
    select(cluster:variable, adj.r.squared, p.value) %>% 
    arrange(site) %>% 
    mutate(adj.r.squared = round(adj.r.squared, 2),
           p.value = round(p.value, 4))

### 2020-02-01 site_map.Rmd
update

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
  # geom_raster(data = MUR, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 5) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub_map, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(13, 23), ylim = c(-36,-26), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  scale_fill_viridis(
    option = "magma",
    name = "Temperature (°C)",
    alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 15.00, y = -33.0,
             size =6, angle = 0, colour = "black") +
    annotate("text", label = "Benguela", x = 14.5, y = -30,
             size = 6, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5),
        axis.text = element_text(size = 12)) +
    guides(fill = guide_colourbar(barheight = 1.00, barwidth = 10)) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.minor = element_line(colour = "NA"),
        panel.grid.major = element_line(colour = "ivory", size = 0.2, linetype = "dotted"),
        legend.direction = "horizontal",
        legend.justification = c(1,0),
        legend.position = c(0.85, 0.70),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5))
site_map

>>>>

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
  # geom_raster(data = MUR, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 5) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub_map, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(13, 23), ylim = c(-36,-26), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  scale_fill_viridis(
    option = "magma",
    name = "Temperature (°C)",
    alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 15.00, y = -33.0,
             size =6, angle = 0, colour = "black") +
    annotate("text", label = "Benguela", x = 14.5, y = -30,
             size = 6, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  scale_colour_Publication()+
  theme_Publication() # R publication theme
  # theme(panel.background = element_rect(fill = "ivory", colour = NA),
  #       panel.border = element_rect(colour = "black", size = 0.5),
  #       panel.grid.major = element_blank(),
  #       panel.grid.minor = element_blank(),
  #       legend.text = element_text(size = 12),
  #       legend.title = element_text(size = 12),
  #       legend.key = element_blank(),
  #       legend.background = element_blank(),
  #       axis.ticks = element_line(size = 0.5),
  #       axis.text = element_text(size = 12)) +
  #   guides(fill = guide_colourbar(barheight = 1.00, barwidth = 10)) +
  # theme(panel.background = element_rect(fill = "ivory", colour = NA),
  #       panel.border = element_rect(colour = "black", size = 0.5),
  #       panel.grid.minor = element_line(colour = "NA"),
  #       panel.grid.major = element_line(colour = "ivory", size = 0.2, linetype = "dotted"),
  #       legend.direction = "horizontal",
  #       legend.justification = c(1,0),
  #       legend.position = c(0.85, 0.70),
  #       legend.text = element_text(size = 8),
  #       legend.title = element_text(size = 8),
  #       legend.key = element_blank(),
  #       legend.background = element_blank(),
  #       axis.ticks = element_line(size = 0.5))
site_map
